---
title: "Topics in Bayesian Computing"
author: |
  | **Class of STAT 946, Spring 2020**
  | **University of Waterloo**
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    includes:
      in_header: preamble.html
bibliography: [applications.bib]
link-citations: true
---

```{r setup, include = FALSE}
user_link <- function(name, username) {
  paste0("[", name, "](https://github.com/", username, ")")
}
```

# BNP for Scalable Signal Monitoring 

## Problem Statement
The Internet of Things(IOT) is made possible by the convergence of cheap data storage, ubiquitous networks, and fully connected sensing devices; all commodity items.  IOT brings with it the possibility to control and monitor processes at scale.  However though statistical learning methods have enjoyed great success in a number of use cases a major barrier to their widespread adoption across the IOT lies in the effort required to achieve useful implementations.  

Consider digital signal anomaly detection.  Automatic identification and warning of abnormal signal indications is a desirable feature for maintainers of large systems.  Typically systems have tens or hundreds of thousands of measured signals; a number that is projected to increase dramatically.  Deploying anomaly detection at scale across such a system may not be economically efficient. Each signal, or group of signals, may have its own unique set of characteristic behaviors and failure modes.  Training a supervised model, or determining and writing the heuristic rules for each is onerous, costly, and inefficient.  Maintaining a collection of model and rules could also be prohibitive in terms of the number of skilled staff such an effort would require.

Thus scalable signal anomaly detection requires general, unsupervised methods with efficient compute.  It is only when a solution requires very little treatment on a per signal basis and consumes a modest set of computational resources that the solution will be of benefit to industry.  

## Addressing Scalability
The Temporally Re-weighted Chinese Restaurant Process (TRCRP) [@saad2018trcrpm] is one BNP based method that could effectively address many of the issues related to scalability.  The originators of the method indicate impressive results with respect to its ability to impute and predict time series data.  The results are achieved without significant modeling, or consideration of parameters, on a per time series basis.  

To test these results, this preliminary investigation made use of the examples provided by the original authors and applied the method to a set of time series from industrial processes. The results provide an intuition for the inner machinations of BNP processes and indicate that there may be merit to the original claims.  Additionally the results have uncovered added utility of the method in the context of identifying anomalous signal behavior. 

The following sections provide a walk through the investigation.  First instructions are provided for a TRCRP test stand setup.  And then a number of investigations of the method are given, each of which provides some intuition and allows for some general conclusions about the utility of the method.

## The Temporally Reweighted Chinese Restaurant Process
TRCRP is a generative temporal extension of the Dirichlet process.  Samples from its posterior are distributed according to a $Normal$ distribution, with and $Normal-InverseGamma$ prior.  In a multivariate setting it is capable of clustering data according to the states which they aquire via the embedded Chinese Restaurant Process(CRP).  It uses a Markov Chain Monte Carlo processes for sampling, and resampling.  

[More to math and description/explanation to come in the paper...]

## Test Stand Tools and Setup
```{r child="bnp/tools.Rmd", echo=T}
```

## Jupyter Application Files
```{r child="bnp/applications.Rmd", echo=T}
```

## Towards a STAT946 Final Project
```{r child="bnp/future.Rmd", echo=T}
```

